### 2021-10-13 plos_latex_template.tex
Rocío: Edits to rule 10

%Sara: I think the last rule should be about the process and reinforce to actually discuss and include diversity as a principle and not as a checklist (as it is on the text). Maybe also something about accountability and permanence. I think that this rule go be together with the rule_organizing_team given that it is relative to the team work and their dynamics.
%Sara: copying Yani comment here -  I like the "accountable and permanent" name. I think that an idea about progressive improvement can be mention here, like improve something every edition and no go back on the conquers goals. Now, to be accountable, you need to be transparent, and you need a clear structure; you get that with the structure of your team, with your declaration and guidelines, and with your action to reinforce those declarations and guidelines (if you have only declarations then you have only empty words, that sound good but you no need to comply. We discuss a lot about this).  For me, one more time, putting together a diverse team is what makes the other thing happened. We can cite The tyranny of structurelessness. The Second Wave, 2(1), 1972. on this rule. Perhaps we can talk about governance.
%ast: i'll put the last version of the tenth rule just to have an idea of how we left this
%past names: Have a bold vision but be ready to compromise when necessary/Aim for progress not perfection
%more people rules that have a continuity/accountability theme
%Aim for Progress, not Perfection
%Plan, balance and keep working to improve inclusion in the next edition of the conference!
%Assess whether equity and inclusion goals were met during the meeting
%Be accountable and permanent
%Use feedback from previous conferences or other conferences in your field to identify barriers to inclusion and plan around them

This rule is a complement to all the other rules. It is important to have a bold vision and clear targets. Some parts might be defined as baseline assumptions that are not up for discussion. However, there will always be compromises. Ideal solutions that meet all our expectations are often not possible. Don't let the perfect be the enemy of good. As a team, this is a challenging journey. Very early on, we tried to recognize that our resources were limited (both in time of the organizing team but also in money). We had to let go of certain aspects that were important to many of us. For an inclusive conference, we need to avoid giving in because considering all aspects seems impossible and burning ourselves and the team out because considering all aspects is actually impossible.

>>>>

% Rocío: main idea: we're not changing everything at the beginning, the conference will not be perfectly inclusive
Do not expect the conference to be perfect. 
Resources, both in time and money, are always limited. 
Most importantly, there are systemic discrimination issues at higher levels (e.g. society, academia) that one conference cannot change. 
There will be resistance, but your courage to make changes will be a step towards a more diverse and inclusive community, and can have a huge impact in the lives and careers of often excluded and minoritized people.

% Rocío: main idea: be part of the process
Diversity and inclusion will be the norm in the long-term if we see conferences as part of the structural change. 
After the conference is over, assess whether equity and inclusion goals were met during the meeting. 
This can be done internally within the organizing team and taking into account the attendees' point of view. 
Identify the things that worked towards your inclusion goals, and try to understand what went wrong and how people were excluded.
Make sure to share the information with future organizers so that they can use it as a starting point and keep working to improve inclusion in the next edition of the conference.

% For many people working with diversity, one typical aim is institutionalizing diversity (Ahmed 2012). However, our aim is also a symptom that diversity and equity are not part of institutions, academic societies, and conferences. This rule is about the process of making diversity and inclusion possible and a complement to all the other rules. We believe we need to be accountable and we need to aim for permanence. Institutionality comes from a set of norms, values, and priorities and these determine who is allowed and how (Ahmed 2012). Our long-term goal is to set new norms, values, and priorities based on diversity. Organizing a diverse conference is part of the process of change. However, we cannot do everything at one conference or a few of them. It is important to have a bold vision and clear targets. Keep in mind that ideal actions are often not possible and resources are limited (both time of the organizing team and money.

% If from the beginning we set diversity goals and actions for the conference, we can use that to be transparent and, later, accountable. Assess whether equity and inclusion goals were met during the meeting. This can be done internally within the organizing team and often also through the conference’s participants. Plan, balance and keep working to improve inclusion in the next edition of the conference. Try to propose permanent data collection to assess whether diversity and inclusion are actually being seen at the conference. We know that diversity and equity are not institutionalized, in fact, the system works to stop those who are changing the system (Ahmed 2019). We will find resistance, but diversity is a school. We also learn more about how people are being excluded, we learn that there are actions we can take to include more, and then, we can set higher goals on how to make inclusion possible.
